---
title: "PS5_Partc num 3"
author: "santiago"
date: "11/7/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
```
# A

```{r}
samples_gen <-function(n){
  list()->list1
  for (i in 1:n){
    #Generatete x1 with n=10 from uniform[0,20]
    runif(25,0,20)->x1
    runif(25,0,20)->x2
    runif(25,0,20)->x3
    runif(25,0,20)->x4
    #Generate errors from standard  normal
    rnorm(25,mean=0,sd=5)->errors1
    data.frame(x1=x1,x2=x2,x3=x3,x4=x4,error=errors1) %>%
      mutate(y= 1- 1*x1 +1*x2-1*x3^2+0.5*x4+error)->list1[[i]]
  }

return(list1)
}

```

## 10 samples

```{r}
samples_gen(10)->obj_10_samples
```

```{r}
#Genearte linear model for each sample
map(.x=obj_10_samples, ~lm(y~x1+x2+I(x3^2)+x4,data=.))->lm10


```

```{r}
vector(mode="numeric", length = 10)->vec1
vector(mode="numeric", length = 10)->vec2
vector(mode="numeric", length = 10)->vec3
vector(mode="numeric", length = 10)->vec4
vector(mode="numeric", length = 10)->vec5

for (i in 1:10){
  lm10[[i]]$coefficients[[1]][1]->vec1[[i]]
  lm10[[i]]$coefficients[[2]][1]->vec2[[i]]
  lm10[[i]]$coefficients[[3]][1]->vec3[[i]]
  lm10[[i]]$coefficients[[4]][1]->vec4[[i]]
  lm10[[i]]$coefficients[[5]][1]->vec5[[i]]
  
}
```

```{r}
#Output the mean for the coeffcicents from n samples
c(mean(vec1),mean(vec2),mean(vec3),mean(vec4),mean(vec5))->mean_n10

#Output the variance for the coefficients from n samples
c(var(vec1),var(vec2),var(vec3),var(vec4),var(vec5))->var_n10
```

```{r}
vector(mode="numeric", length = 10)->vec1
vector(mode="numeric", length = 10)->vec2
vector(mode="numeric", length = 10)->vec3
vector(mode="numeric", length = 10)->vec4
vector(mode="numeric", length = 10)->vec5

for (i in 1:10){
  lm10[[i]]$coefficients[[1]][1]-1->vec1[[i]]
  lm10[[i]]$coefficients[[2]][1]+1->vec2[[i]]
  lm10[[i]]$coefficients[[3]][1]-1->vec3[[i]]
  lm10[[i]]$coefficients[[4]][1]+1->vec4[[i]]
  lm10[[i]]$coefficients[[5]][1]-0.5->vec5[[i]]
  
}
c(vec1,vec2,vec3,vec4)->terms10
sum(terms10^2)/10->MSE_B_10


```

Below are the mean betas, the variances and MSE FOR 10 SAMPLES.
```{r}
mean_n10
var_n10
MSE_B_10

```

### 500 samples

```{r}
samples_gen(500)->obj_500_samples
```

```{r}
#Genearte linear model for each sample
map(.x=obj_500_samples, ~lm(y~x1+x2+I(x3^2)+x4,data=.))->lm500


```

```{r}
vector(mode="numeric", length = 500)->vec1
vector(mode="numeric", length = 500)->vec2
vector(mode="numeric", length = 500)->vec3
vector(mode="numeric", length = 500)->vec4
vector(mode="numeric", length = 500)->vec5

for (i in 1:500){
  lm500[[i]]$coefficients[[1]][1]->vec1[[i]]
  lm500[[i]]$coefficients[[2]][1]->vec2[[i]]
  lm500[[i]]$coefficients[[3]][1]->vec3[[i]]
  lm500[[i]]$coefficients[[4]][1]->vec4[[i]]
  lm500[[i]]$coefficients[[5]][1]->vec5[[i]]
  
}
```

```{r}
#Output the mean for the coeffcicents from n samples
c(mean(vec1),mean(vec2),mean(vec3),mean(vec4),mean(vec5))->mean_n500

#Output the variance for the coefficients from n samples
c(var(vec1),var(vec2),var(vec3),var(vec4),var(vec5))->var_n500
```

```{r}
vector(mode="numeric", length = 500)->vec1
vector(mode="numeric", length = 500)->vec2
vector(mode="numeric", length = 500)->vec3
vector(mode="numeric", length = 500)->vec4
vector(mode="numeric", length = 500)->vec5

for (i in 1:500){
  lm500[[i]]$coefficients[[1]][1]-1->vec1[[i]]
  lm500[[i]]$coefficients[[2]][1]+1->vec2[[i]]
  lm500[[i]]$coefficients[[3]][1]-1->vec3[[i]]
  lm500[[i]]$coefficients[[4]][1]+1->vec4[[i]]
  lm500[[i]]$coefficients[[5]][1]-0.5->vec5[[i]]
  
}
c(vec1,vec2,vec3,vec4,vec5)->terms500
sum(terms500^2)/500->MSE_B_500


```

Below are the mean betas, the variances and MSE FOR 500 SAMPLES.
```{r}
mean_n500
var_n500
MSE_B_500

```
```{r}
mean_n10
var_n10
MSE_B_10
mean_n500
var_n500
MSE_B_500
```

Once again, the estimated coefficients accurately represent the population parameters.The intercept seems to be the less accurate for 10 samples. We also see that as the number of samples increases the mean squared error of B decreases. Essentially, we see very similar results as we did in the linear case.

# B

```{r}
b1list10 <- vector(mode = "numeric", length=10)
for (i in 1:10){
  lm10[[i]]$coefficients[[2]][1]->b1list10[[i]]
  
}
plot(b1list10)
abline(h=mean_n10[[2]])
```


```{r}
b1list500 <- vector(mode = "numeric", length=500)
for (i in 1:500){
  lm500[[i]]$coefficients[[2]][1]->b1list500[[i]]
  
}
plot(b1list500)
abline(h=mean_n500[[2]])
```

# C 

We can clearly see that increasing the number of samples increases the accuracy of our predicted estimate and also reduces the Mean squared error of (beta_hat) on the margin. We also find that the results are very similar to what we saw in the linear case.