---
title: "Estimating Mathematical Constant using Montecarlo"
author: "santiago"
date: "1/27/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Estimate log2 by estimating $\int_0^1 \frac{1}{1+x}dx$.

How to estimate $\int_0^1 \frac{1}{1+x}dx$ using simulation?

$$\int_0^1 \frac{1}{1+x}dx = E(\frac{1}{1+X}),  where X \sim Unif(0, 1)$$ 
Estimate $$E(\frac{1}{1+X}),  where X \sim Unif(0, 1)$$ by simulation.

Estimate the Expected value (population mean) use sample mean of Y = 1/(1+X), denote the sample mean of Y as y_bar. also, find the sample std.dev. of Y=1/(1+X), denote the sample std.dev. as s_y. Then, we can construct the CI for E(Y): y_bar +/- z*s_y/sqrt(n)

Generate/Compute samples for y_i = 1/(1+X_i) by simulation.

Generate samples for x_i ~ Unif(0, 1) by simualtion. i = 1, 2. ...., 10,000 (sample size n)

```{r}
estimate_log2 <- function(seed = 29, n = 10000, interval= 0.95){
    # set seed for reproducibility
    set.seed(seed)
    
    # generate x
    x <- runif(n, min = 0, max = 1)
    
    #generate samples, i.e., transform x
    y <- 1/(1+x)
    
    
    # Point estimates from sample
    mean(y) -> EY #Calculate estimate for ln2
    #Calculate SE
    sd(y)->sdY 
    sdY/sqrt(n) -> se
    
    
    c.i <- c(EY-se*qnorm(p=interval),EY+se*qnorm(p=interval))
    return(c(c.i[1],"<=",EY,"<=",c.i[2]))
}

estimate_log2()


log(2)
```



